%-------------------------
% Resume in Latex
% Author : Sanjay Subramaniam
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/sanjaymaniam/}{\Large Sanjay Subramaniam}} & Email : \href{mailto:sanjaysubramaniam99@gmail.com}{sanjaysubramaniam99@gmail.com}\\
  \href{https://www.linkedin.com/in/sanjaymaniam/}{https://www.linkedin.com/in/sanjaymaniam/} & Mobile : +91-735-8850-853 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Manipal Institute of Technology}{Manipal, Karnataka}
      {Bachelor of Technology in Mechatronics Engineering, Minor in Digital Marketing}{2017-2021}
      \begin{itemize}
        \item Embedded Systems at Project Manas, Manipal’s official AI Robotics team. Won a second prize at Intelligent Ground Vehicle Competition 2018 , Oakland University, Michigan.
        \item Represented a class of 80 sophomores to the Student Council for a year. Responsible for organizing lectures, coordinating between faculty and students and answering administrivia.
        \item Relevant Coursework: Digital Integrated Circuits, Embedded Systems, Linux and Shell Scripting.
      \end{itemize}

    \resumeSubheading
      {Suguna Pip School}{Coimbatore, Tamil Nadu}
      {Physics, Math, Chemistry and Computer Science}{2015-2017}
      \begin{itemize}
        \item Scored a 90\% in 12th grade CBSE board examinations.
        \item Awarded the Outstanding Rylarian award by the Rotary Club of Coimbatore, TexCity for leadership and public speaking skills.
        \item Delegate at Indian International Model United Nations, Kodaikanal.
      \end{itemize}
      
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Aekam Labs}{Coimbatore, Tamil Nadu}
      {Lead Instructor}{Feb 2021 - Present}
      \resumeItemListStart
        \resumeItem{Front-end Development}
          {Coached high school and university students in the basics of front-end web development. Helped them start their open-source projects, and kick-started their coding journey.}
        \resumeItem{Open-source projects co-ordination}
          {Organized and coordinated development of Aekam's open-source efforts. Technologies used: .NET, Django, Tailwind CSS, Bootstrap and Angular.}
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
    
    \resumeSubheading
      {Dreamtraps Media}{Manipal, India}
      {Freelance Writer}{Feb 2021 - Present}
      \resumeItemListStart
        \resumeItem{Copywriting}
          {Generated around INR 10,000 a month from freelance writing projects.}
        \resumeItem{Independent blogging}
          {Averaged around 200 page views a week. Wrote over 30,000 words over the period.}
      \resumeItemListEnd


    \resumeSubheading
      {Dubai Cable Company}{Abu Dhabi, UAE}
      {PLC Programming Intern}{Jun. 2019 -- Jul. 2019}
      \resumeItemListStart
        \resumeItem{Alarm System for Sheathing Line}
          {Built a Siemens S7-300 PLC based alarm system using Ladder Logic for a cable insulation line.}
        \resumeItem{Industrial Training}
          {Worked with industry professionals and technicians to learn about standard production, testing and maintenance processes.}
      \resumeItemListEnd
      
     \resumeSubheading
      {Project Manas: AI Research \& Robotics Team}{Manipal, Karnataka}
      {Jr. Embedded Systems Engineer}{Dec. 2017 -- Nov. 2018}
      \resumeItemListStart
        \resumeItem{Intelligent Ground Vehicle Competition 2018}
          {Our team won a second prize at Intelligent Ground Vehicle Competition 2018, Oakland University, Michigan for the IOP challenge.}
        \resumeItem{Arduino Programming}
          {Interfaced, calibrated and debugged quadrature wheel encoders for velocity and distance estimation. Responsible for assessing and debugging problems in the embedded and hardware suite that went on the robot.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{hermione (Ongoing)}
      {Open-source alternative to Goodreads. Using Django and React for most purposes.}
    \resumeSubItem{kindlerWeb}
      {Open source tool to curate Kindle highlights. Used Django, PostgreSQL and SQLite.}
    \resumeSubItem{noobNet}
      {Basic Deep Learning Framework built using pure C++ to understand fundamentals}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
